Hydrogen Epoch of Reionization Array (HERA)

### 2016-04-13 manuscript.tex
sec 5 and added proto-site section
updated atten spec plot

To get 60 dB at 60 ns we may interpret those lines in one of two ways:  (1) set the spec on how much attentuation per reflection is needed and (2) at a fixed attenuation/reflection, what diameter we need.  For 1 round-trip, for the assumed $f/D$ over the diameters of interest, all delays are less than 60 ns, so it provides no constraint.  For
3 round-trips, all diameters exceed 60 ns, so the attenuation should be less than 60 dB for that path-length.  The case for 2 round-trips provides a constraint on attenuation and diameter, which is discussed at length in \cite{elementmemo}.
To estimate, it was assumed that the main reflection time constant was due to the standing waves between the feed and vertex of the parabola and that each reflection redirected about -15 dB of the total power in each reflection for additional standing wave power, which leads to a diameter of about 14m.

As a key specification, this has been a focus of study with our prototypes and a series of papers based on analysis and measurements have been produced to provide much more rigor than this simple early analysis \citep{ewall-wice_et_al2016-EoXLimits,neben_et_al2016,thyagarajan_et_al2016,patra_et_al0216}.  The simple specification set above more appropriately becomes a series of curves for attenuation and delay at different wavenumbers for realistic foreground models.  Fig \ref{fig:delayspec}, adapted from \cite{thyagarajan_et_al2016}, shows the results at $k$ = 0.2 $h$/Mpc for the adopted design.  The analysis shows that for $k>0.15 h/$Mpc, HERA should be able to detect the EoR.  We also see that the initial simple ``60@60'' specification was an overly restrictive, however was a good initial goal.  The analysis also indicates which baselines produce the best information on different scales.

@@

\subsection{Antenna}
\label{sec:antenna}
\vspace{-5pt}

>>>>

To get 60 dB at 60 ns we may interpret those lines in one of two ways:  (1) set the spec on how much attenuation per reflection is needed and (2) at a fixed attenuation/reflection, what diameter we need.  For 1 round-trip, for the assumed $f/D$ over the diameters of interest, all delays are less than 60 ns, so it provides no constraint.  For
3 round-trips, all diameters exceed 60 ns, so the attenuation should be less than 60 dB for that path-length.  The case for 2 round-trips provides a constraint on attenuation and diameter, which is discussed at length in \cite{elementmemo}.
To estimate, it was assumed that the main reflection time constant was due to the standing waves between the feed and vertex of the parabola and that each reflection redirected about -15 dB of the total power in each reflection for additional standing wave power, which leads to a diameter of about 14m.

As a key specification, this has been a focus of study with our prototypes and a series of papers based on analysis and measurements have been produced to provide much more rigor than this simple early analysis \citep{ewall-wice_et_al2016-EoXLimits,neben_et_al2016,thyagarajan_et_al2016,patra_et_al0216}.  The simple specification set above more appropriately becomes a series of curves for attenuation and delay at different wavenumbers for realistic foreground models.  Fig \ref{fig:delayspec}, adapted from \cite{thyagarajan_et_al2016}, shows the results at $k$ = 0.2 $h$/Mpc for the adopted design.  The analysis shows that for $k>0.15 h/$Mpc, HERA should be able to detect the EoR.  We also see that the initial simple ``60@60'' specification was a overly conservative, however it served as a good initial goal.  The analysis also indicates which baselines produce the best information on different scales.

@@

%\subsection{Site}
%\label{sec:site}
HERA is located at the Karoo Astronomy Reserve.

\subsection{Antenna}
\label{sec:antenna}
